\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

The thesis \textit{''Optimizing the geometry of a breakwater connected to large floating structures''} represents the concluding part of the master Marine Technology at Delft University of Technology. The past 10 months of working on the project went with ups and downs, but as I write this as the graduation date approaches, I look back with a smile. Proud of the results that I can present to you, the reader, in collaboration with Peter Wellens (TU Delft), Bas Hofland (TU Delft) and Joep van der Zanden (MARIN).\\
\\
Although this project began during the Covid-19 pandemic, which brought many changes and required some adaptation, the phase of finding a thesis project and formulating research questions went quite smoothly. As Peter had already supervised my Bachelors thesis a few years ago, I knew we would have a pleasant and efficient working collaboration, however, already realising back then there was still a lot I could learn from him. Furthermore, I was intrigued with MARIN's research from the beginning of my studies, so this was the perfect time to establish a collaboration and experience working in an institute with so much knowledge. After discussing several possible research topics, I was immediately triggered by the topic Joep proposed: the feasibility of inhabiting floating islands by designing an efficient floating breakwater.\\
\\
Every day I am still happy with the choices I made a year ago and am grateful to all the committee members and could not have wished for a more enjoyable collaboration. A special thanks to Bas Hofland for the clear and concise feedback. Many thanks to Joep van der Zanden for the incredible amount of support he gave me and the many quality conversations that led to it and to Peter Wellens for the excellent feedback and for making me highly motivated to pursue every time I walked out of his office. \\
\\
This dissertation will be my last work at this university, at least as a student. However, I would like to continue working in the field, expand my knowledge and contribute with a positive impact on climate, nature, and humanity.\\
\\

But for now, enjoy the read!


\begin{flushright}
{\makeatletter\itshape
    \ifdefvoid{\@author@short}{\@author}{\@author@short} \\
    Delft, \monthname{} \the\year{}
\makeatother}
\end{flushright}
