\section{Discussion}
\label{sec: discussion moving}
%from H3


-first thing to notice is that the dependency of most factors on the mean wave drift force is very different in comparison with the capitve design optimization. Figure \ref{fig: perturbation R1 DI1 moving H3} shows a complete different trend for the variation of WL (the position of the waterline w.r.t. the breakwater. Its optimum is still beneath the waterline. \\

-trend of negative mean wave drift forces still there, but less visible-->maybe because due to pressure difference the breakwater moves in x-direction to counteract, therefore the mean pressure difference between fore and aft of the breakwater less present and therefore not so much negative mean wave drift force. (also observed in results of \citet{Zanden2021})


%from H9

-first time the optima based on a minimal mean wave drift force are placed above the water, is with moving H9! explanation: lots of stability is desired due to the heavy waves. small draught, means small displacement, means large BM.


%kritiek op mezelf
-hinge point stiffness\\
-response surfaces for (ff=0.01 , tf = 0.99) and (ff=0.99 and tf = 0.99) varies a lot, while the shape of the structure does not.\\
% -goedkopere simulaties waren zeker mogelijk
% -betere optimalisatie (die shit van auke van der ploeg mentionen)
% -only one, regular wave at the time, efffect might be really really different in real live, with an irregular wave spectrum
-spring term linearly increases with deflection, so with large deflection (e.g. due to second-order force) still leads to a stiff system (at least in one direction). In reality, floating island will behave different on hinge point, it will translate and rotate itself as well. possibility: include island in optimisation but may make it expensive

% -veermatrix neemt lineair toe met uitwijking, dus bij een erg grote uitwijking is er eigenlijk alsnog een erg stijf systeem (as least in one direction), in reality the floating island will float with the breakwater into that direction and will not lay captive. possibility: include island in optimisation but may make it expensive

-second design iteration is required

-peter--> minder transmissie door groot objet eracther, meer reflectie, meer drift forces en gedrag brekende golven worden daardoor ook beïvnloedt

\section{Conclusions}
\label{sec: conclusions moving}